Untitled

### 2020-03-18 Rmd/World_Map_Compatibility_Systems.Rmd
Compatibility system plot

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
#WORLDPLOT WITH BREEDING SYSTEMS

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,15,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

@@

#Group breeding system per metaweb or web
all_summary_breeding_system <- dcast(all_species_per_network,Id~Breeding_system,value.var = "Breeding_system")

#Cleaning NA and one unfinished network
all_summary_breeding_system <- all_summary_breeding_system[-c(6,30),]

#Removing ".csv" from the Id to megere with coordinates
all_summary_breeding_system$Id <- gsub("\\..*","",all_summary_breeding_system$Id)

@@

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_breeding_system)

data_merged[,c(3,4,6:19)] <- sapply(data_merged[,c(3,4,6:19)],as.numeric)
sapply(data_merged, class)
data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)
#Prepare data for plotting
data_merged$Hermaphroditism <- data_merged$hermaphrodite
data_merged$Dioecy <- data_merged$androdioecious + data_merged$androgynodioecious + data_merged$dioecious+
  data_merged$gynodioecious + data_merged$monoecious_dioecious + data_merged$`polygamo-dioecious`+
  data_merged$subdioecious

data_merged$Monoecy <- data_merged$andromonoecious + data_merged$gynomonoecious + data_merged$monoecious
+ data_merged$submonoecious

data_merged_sub <- data_merged[, c(1:6, 20:22)]
#Plot data
world <- map_data('world')

@@

@@

 labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
 "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +

>>>>

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA

setwd("~/R_Projects/Reproductive Traits")

Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,22,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

@@

#Group breeding system per metaweb or web
all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")

#Cleaning NA and one unfinished network
all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]

all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible) 
all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
#Removing ".csv" from the Id to megere with coordinates
all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)

@@

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_compatibility_system)

data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)

#I have done this in other code for other reasons
#I'm going to maintain it
data_merged_sub <- data_merged
#Plot data
world <- map_data('world')

@@

data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
str(data_merged_sub_ord)

@@

 labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility systems",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
